VM-Centric Snapshot Deduplication for Converged Cloud Architectures

### 2014-07-18 snapshot_system/paper.tex
re
add bg

\documentclass{acm_proc_article-sp}
\usepackage{mathptmx}
\usepackage[colorlinks,linkcolor=red,anchorcolor=blue,citecolor=green,urlcolor=black]{hyperref}
\usepackage{subfigure}
\usepackage{epsfig}
\usepackage{multirow}
\usepackage{array}
\usepackage{breqn}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usepackage{sansmath}
\usepackage{booktabs}
\usepackage{soul}
\pgfplotsset{compat=1.5}
\DeclareGraphicsExtensions{.pdf}

@@

%\linespread{.98} % to squeeeze lines and put figures in same page
\begin{document}

%\title{VM-Centric Deduplication with Fault Isolation for Virtual Machine Snapshot Backup }
%Collocated Snapshot Backup with VM-Centric Deduplication in the Cloud}

%with Fault Isolation 
\title{
VM-Centric  Snapshot Deduplication  for Converged Cloud Architectures} 
%VM-Centric  Deduplication  with Fault Isolation for Snapshot Backup in the Cloud
\author{
  Wei Zhang$^{\star}$, Daniel Agun$^\star$, Tao Yang$^\star$, Rich Wolski$^{\star}$, and  Hong Tang$^\dagger$\\
  $^\star$University of California at Santa Barbara \\
  $^\dagger$Alibaba Inc. \\
%  \{wei, dagun,tyang,rich\}@cs.ucsb.edu, hongtang@alibaba-inc.com
}
  %{\normalsize $^\star$University of California at Santa Barbara} \ \ {\normalsize$^\dagger$Alibaba Inc.} \\

@@

\category{D.2.8}{Information Systems}{Information Storage Systems}
\terms{Design, Experimentation, Performance, Reliability}

\keywords{Virtual machine images, snapshot backup and deletion, source-side deduplication, 
cloud clusters and distributed architectures} % NOT required for Proceedings

\input{paper_intro}
\input{paper_background}
\input{paper_dedup}
\input{paper_del}
\input{paper_arch}
\input{paper_eval}
\input{paper_conc}
\appendix
\input{paper_analysis}

%\linespread{.97} % to squeeeze lines and put figures in same page
\bibliographystyle{abbrv}
\bibliography{library,dedup1}
\end{document}

>>>>

\documentclass[10pt,reprint]{socc14}
\usepackage{mathptmx}
\usepackage[colorlinks,linkcolor=red,anchorcolor=blue,citecolor=green,urlcolor=black]{hyperref}
\usepackage{subfigure}
\usepackage{epsfig}
\usepackage{multirow}
\usepackage{array}
\usepackage{breqn}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usepackage{sansmath}
\usepackage{booktabs}
\usepackage{soul}
\pgfplotsset{compat=1.5}
\DeclareGraphicsExtensions{.pdf}

@@

%\linespread{.98} % to squeeeze lines and put figures in same page
\begin{document}
\special{papersize=8.5in,11in}
\setlength{\pdfpageheight}{\paperheight}
\setlength{\pdfpagewidth}{\paperwidth}
\conferenceinfo{Submission to SoCC '14}{October, 2014, Seattle, WA, USA}
\copyrightyear{2014}
\copyrightdata{978-1-nnnn-nnnn-n/yy/mm}
\doi{nnnnnnn.nnnnnnn}
%\title{VM-Centric Deduplication with Fault Isolation for Virtual Machine Snapshot Backup }
%Collocated Snapshot Backup with VM-Centric Deduplication in the Cloud}

%with Fault Isolation 
\title{
VM-Centric  Snapshot Deduplication  for Converged Cloud Architectures} 
%VM-Centric  Deduplication  with Fault Isolation for Snapshot Backup in the Cloud
\authorinfo{
  Wei Zhang$^{\star}$, Daniel Agun$^\star$, Tao Yang$^\star$, Rich Wolski$^{\star}$, and  Hong Tang$^\dagger$\\
  $^\star$University of California at Santa Barbara \\
  $^\dagger$Alibaba Inc. \\
%  \{wei, dagun,tyang,rich\}@cs.ucsb.edu, hongtang@alibaba-inc.com
}
  %{\normalsize $^\star$University of California at Santa Barbara} \ \ {\normalsize$^\dagger$Alibaba Inc.} \\

@@

\category{D.2.8}{Information Systems}{Information Storage Systems}
\terms
Design, Experimentation, Performance, Analysis

\keywords
Virtual machine images, snapshot backup and deletion, source-side deduplication, cloud clusters and distributed architectures

\input{paper_intro}
\input{paper_background}
\input{paper_dedup}
\input{paper_del}
\input{paper_arch}
\input{paper_eval}
\input{paper_conc}

%\linespread{.97} % to squeeeze lines and put figures in same page
\appendix
\input{paper_analysis}
\bibliographystyle{abbrvnat}
\bibliography{library,dedup1}
\end{document}

### 2014-07-18 snapshot_system/paper_background.tex
add bg
change bg

%Cross-VM chunk sharing also complicates 
Snapshot deletion occurs frequently since  snapshots expire regularly
and reference counting is required to identify chunks that are no longer used.
The grouped mark-and-sweep approach~\cite{Guo2011}
is effective for deletion, but still carries a significant cost, especially in a distributed 
setting.   This is because any data chunk can be used by any snapshot
of virtual machines in a large cloud cluster and there are multiple rounds of  extensive I/O involved
to scan through the metadata of snapshots to determine if a chunk has been used or not.
As the number of virtual  machines increases, the cost becomes even worse.
%~\cite{Guo2011,Fabiano2013}  
%to count if a data chunk is still shared by other snapshots.

@@

Another disadvantage of cross-VM sharing is that it complicates 
snapshot deletion, which occurs frequently because snapshots expire regularly.
Several well developed garbage collection methods do not apply to the
converged virtualized architecture due to various environment and resource limitations:
Grouped mark-and-sweep~\cite{Guo2011} is an effective approach by tracking
the dependencies from data containers to metadata groups, such that only a subset of
metadata needs to be scanned in order to reclaim the garbage in any given data container.
However, data in VM environment tend to be highly dedupable which means
such dependency could be extensive, therefore scanning a large subset of metadata still carries a significant cost,
 especially in a distributed setting.
Perfect hashing~\cite{Fabiano2013} provides a very memory efficient way to represent a large set of
hashes in a compact form, however, it still requires the scan of all data hashes before any garbage could begin,
which limits its application to only offline batch garbage collection. In addition, it requires a centralized location
to store the hashing result which couldn't be hold anywhere in our converged architecture.
%to count if a data chunk is still shared by other snapshots.

>>>>

Another disadvantage of cross-VM sharing is that it complicates
snapshot deletion, which is the garbage collection in VM environment
that occurs frequently because snapshots expire regularly.
Several well developed garbage collection methods do not apply to the
converged virtualized architecture due to various environment and resource limitations:
Grouped mark-and-sweep~\cite{Guo2011} is an effective approach by tracking
the dependencies from data containers to metadata groups, such that only a subset of
metadata needs to be scanned in order to reclaim the garbage in any given data container.
However, data in VM environment tend to be highly dedupable which means
such dependency could be extensive, therefore scanning a large subset of metadata still carries a significant cost,
 especially in a distributed setting.
Perfect hashing~\cite{Fabiano2013} provides a very memory efficient way to represent a large set of
hashes in a compact form, however, it still requires the scan of all data hashes before any garbage collection could begin,
which limits its application to only offline batch garbage collection. In addition, it requires a centralized location
to store the hashing result which is still too big to be hold anywhere in a converged architecture.

%Cross-VM chunk sharing also complicates 
% Snapshot deletion occurs frequently since  snapshots expire regularly
% and reference counting is required to identify chunks that are no longer used.
% The grouped mark-and-sweep approach~\cite{Guo2011}
% is effective for deletion, but still carries a significant cost, especially in a distributed
% setting.   This is because any data chunk can be used by any snapshot
% of virtual machines in a large cloud cluster and there are multiple rounds of  extensive I/O involved
% to scan through the metadata of snapshots to determine if a chunk has been used or not.
% As the number of virtual  machines increases, the cost becomes even worse.
%~\cite{Guo2011,Fabiano2013}  
%to count if a data chunk is still shared by other snapshots.

@@

Another disadvantage of cross-VM sharing is that it complicates 
snapshot deletion, which occurs frequently because snapshots expire regularly.
Several well developed garbage collection methods do not apply to the
converged virtualized architecture due to various environment and resource limitations:
Grouped mark-and-sweep~\cite{Guo2011} is an effective approach by tracking
the dependencies from data containers to metadata groups, such that only a subset of
metadata needs to be scanned in order to reclaim the garbage in any given data container.
However, data in VM environment tend to be highly dedupable which means
such dependency could be extensive, therefore scanning a large subset of metadata still carries a significant cost,
 especially in a distributed setting.
Perfect hashing~\cite{Fabiano2013} provides a very memory efficient way to represent a large set of
hashes in a compact form, however, it still requires the scan of all data hashes before any garbage could begin,
which limits its application to only offline batch garbage collection. In addition, it requires a centralized location
to store the hashing result which is still too big to be hold anywhere in a converged architecture.

%to count if a data chunk is still shared by other snapshots.
